---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r echo=TRUE}
unzip("activity.zip")

activity <- read.csv("activity.csv")
dim(activity)
head(activity)

```


## What is mean total number of steps taken per day?

1) Histogram with total number of steps taken per day

```{r echo=TRUE}
activity.data <- aggregate(steps ~ date, data=activity, FUN = sum)

barplot(activity.data$steps, names.arg = activity.data$date, xlab = "Date",
        ylab = "Steps")
```

2) Calculate and report mean and median total number of steps taken per day?

```{r echo=TRUE}
print("Mean total number of steps taken per day:")
mean(activity.data$steps)
print("Median total number of steps taken per day:")
median(activity.data$steps)
```


## What is the average daily activity pattern?
1) Make a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r echo=TRUE}
library(ggplot2)
activity.interval <- aggregate(steps ~ interval, data=activity, FUN = mean)
ggplot(activity.interval, aes(x=activity.interval$interval, y=activity.interval$steps)) + geom_line()+
  ylab("Steps") + xlab("Interval")
```

2) Which 5 minutes intervals contains the maximum number of steps?

```{r echo=TRUE}
activity.interval$interval[which.max(activity.interval$steps)]

```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
